% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Tianyi Li}

\basicInfo{
  \email{noclyt@gmail.com} \textperiodcentered\
  \phone{(+1) 315-898-6611} \textperiodcentered\
  % \homepage[www.noclyt.com]{https://www.noclyt.com}
  \linkedin[LinkedIn]{https://www.linkedin.com/in/noclyt}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Syraucse University}, Syraucse,  America}{Jun. 2017 --
  Dec. 2018}
\textit{M.S.} in Computer Science (CS)

\datedsubsection{\textbf{Shandong Agricultural University}, Shaanxi, China}{Sep.
  2011 -- Jul. 2015}
\textit{B.S.} in Computer Science (CS)

\section{\faUsers\ Intership \& Projects}
\datedsubsection{\textbf{Alibaba Inc.} Beijing, China}
{Jul. 2014 -- May. 2015}
\role{Algorithm Engineer}{ Anti-fraud Group }
\begin{itemize}
  \item Participated to build Alipay Account Risks Model for 1.2 billion
    accounts by machine learning.
  \item Implemented Online Random Forests algorithm with C++. Increased accuracy by 10\% on fraud
    datasets than old Random Forests algorithm.
  \item
    Developed an interactive semi-automatic data analysis GUI tool for feature
    selection and data visualization, with Python and Qt.
  \item
    Became familiar with ETL on hadoop, modeling by machine learning algorithms
    and testing models on big data.
\end{itemize}

\datedsubsection{\textbf{Keystroke Dynamics Based on Support VectorMachine}  } {Dec. 2014 -- Jun. 2015}
\role{Python} {Graduation Thesis}
\begin{itemize}
\item
  Studied current research status of biological recognition and keystroke dynamics.
\item
  Implemented an One Class SVM anomaly detection model with keystroke dynamics datasets.
\item
  Designed experiments to improve accuracy of OC-SVM anomaly detection model.
\end{itemize}


\datedsubsection{\textbf{Malware APP Prediction Based on Machine Learning}  } {Dec. 2013 -- Apri. 2014}
\role{Python Android} {Student Research Training Project}
\begin{itemize}
\item
  Built a prediction model based on Random Forests algorithm to predict whether
  android APP is malware.
\item
  Implemented a web crawler with Python to download android apps from different appstores.
\item
  Familier with Androguard to decompile android apps with to extract features.
\item
  Designed a group of experiments to select features. Improved accuracy to 95 \%
  finally.

\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Main Programming Languages: C++ == Python > Java > Node.js
  \item Others: JSP, Qt, Android, \LaTeX, Emacs
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Silver Medal}, 2013 ACM/ICPC China Tonghua Invitational Programming Contest }{May. 2013}
\datedline{\textit{Honorable Mention} of Mathematical Contest in Modeling} {Jan. 2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://www.noclyt.com
  \item GitHub: https://github.com/noclyt
  \item Languages: English - ordinary, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
